Bulk Semantic Annotation with a Partially Known Knowledge Base

### 2024-12-11 doc/cicm25-sysdesc/sysdesc.tex
abstracct

\title{Bulk Semantic Annotation with a Partially Known Knowledge Base}
\author{Michael Kohlhase, Jan Frederik Schaefer}
\institute{Computer Science, FAU Erlangen N\"urnberg, Germany}
\begin{document}
\maketitle
\begin{abstract}
tbw
\end{abstract}

>>>>

\title{Bulk Semantic Annotation with a Partially Known Knowledge Base}
\author{Michael Kohlhase, Jan Frederik Schaefer}
\institute{Computer Science, FAU Erlangen N\"urnberg, Germany}
\begin{document}
\maketitle
\begin{abstract}
  Semantic Annotations can be utilized for learning support services in technical
  documents. The resulting active documents support more direct and personalized
  interaction with the knowledge conveyed, but require a large investment in the authoring
  process.

  In this paper we discuss the nature of the semantic authoring problem and argue that
  while sharing aspects of classical, informal authoring and formal authoring, it is a
  problem of its own that needs special editing support facilities. We present a simple
  utility that supports the process of annotating technical terms with semantic references
  to a flexiformal content commons that enhances annotation productivity by almost an
  order of magnitude.
\end{abstract}
